---
title: "Diversify Digest"
author: admin
date: Sys.Date
output: md_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')

library(tidyverse)
library(lubridate)

#today <- Sys.Date()

raw_data <- read_csv(paste0("../data/raw", today, ".csv"))

#Category terms----
LGBT_terms <- c("Lgbt|Trans |Transgender|Queer|Sexual Minorit|Gender Minorit|Gender Ident|Sexual Orientation")

race_terms <- c("Urm|Race|Ethnicity|Ethnic|Black|Asian|Native|Indige|Hurm|Immigrant|Racial|Latin|Hispanic|Minority|Racism")

disabil_terms <- c("Disabil|Ability|Deaf|Blind|Wheelchair|Autis|Neurodiverse|Accessibility|Mental Illness")

women_terms <- c("Gender|Women|Female")

edu_terms <- c("Education|Academics|High School|Elementary|Middle School|School|College Grad|Classroom|Learning|Pedagog|Teach")

health_terms <- c("Healthcare|Health|Care|Physician|Illness|Disease|Pain|Medic|Provid")

acad_terms <- c("Grad|Postdoc|Faculty|Academia|Research|Academy|Journal|Publish|Public|Cite|Citation|Author|Academic|Review|Higher Ed|Peer Review")

ment_terms <- c("Mentor|Network")

crt_terms <- c("Critical Race|Crt|Race Theory")

syst_terms <- c("System|Construct|Frame")

bias_terms <- c("Bias|Implicit|Stereotype")

#Categorize titles & generate string----
cite_df <- raw_data %>% mutate(full_cite = paste0("[", title, "](", url, ") ", author, "\n"),
                               race = str_detect(title, race_terms),
                               LGBT = str_detect(title, LGBT_terms),
                               disabil = str_detect(title, disabil_terms),
                               women = str_detect(title, women_terms),
                               edu = str_detect(title, edu_terms),
                               health = str_detect(title, health_terms),
                               academy = str_detect(title, acad_terms),
                               mentor = str_detect(title, ment_terms),
                               crt = str_detect(title, crt_terms),
                               systems = str_detect(title, syst_terms),
                               bias = str_detect(title, bias_terms),
                               dei = if_else(str_detect(title, "Diversity") & str_detect(title, "Inclusion"), TRUE, FALSE))

#Identify top 10 keywords----
`%not_in%` <- Negate(`%in%`)

preposition <- c("and", "of", "the", "a", "as", "in", "with", "can", "be", "to", "for", "without", 
                 "does", "new", "is", "also", "we", "he", "or", "on", "these", "onward", "at", "by", "from", "an ")

titles <- raw_data %>% 
  mutate(title = str_replace_all(title, "[:punct:]", ""),
         title = str_replace_all(title, "[:digit:]", ""),
         title = str_to_lower(title)) %>% 
  pull(title) 
  
words <- str_split(titles, " ") 

words_freq <- words %>% unlist() %>% as_tibble()

keywords <- words_freq %>% 
  filter(value %not_in% preposition) %>% 
  group_by(value) %>% 
  summarise(n = n()) %>% arrange(desc(n)) %>% head(n = 10) %>% pull(value)
```
\-\-\- 

title: `r paste0(month(today, label = TRUE), " ", day(today), " Digest")`

date: `r today`

authors: 

\-\-\- 

{{% toc %}}

### Sexual and Gender Minorities (e.g, LGBTQA+) ##
```{r lgbt_setup, include=FALSE}

LGBT_list <- cite_df %>% filter(LGBT == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r LGBT_list`

### Race/Ethnicity ##
```{r race_setup, include=FALSE}

race_list <- cite_df %>% filter(race == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r race_list`

{{% toc %}}

### Disabilities ##
```{r disabil_setup, include=FALSE}

disabil_list <- cite_df %>% filter(disabil == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r disabil_list`

{{% toc %}}

### Women ##
```{r women_setup, include=FALSE}

women_list <- cite_df %>% filter(women == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r women_list`

{{% toc %}}

### Education ##
```{r edu_setup, include=FALSE}

edu_list <- cite_df %>% filter(edu == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r edu_list`

{{% toc %}}

### Healthcare ##
```{r health_setup, include=FALSE}

health_list <- cite_df %>% filter(health == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r health_list`

{{% toc %}}

### Academia & Publishing ##
```{r acad_setup, include=FALSE}

acad_list <- cite_df %>% filter(academy == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r acad_list`

{{% toc %}}

### Mentoring ##
```{r ment_setup, include=FALSE}

ment_list <- cite_df %>% filter(mentor == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r ment_list`

{{% toc %}}

### Implicit Bias & Stereotypes ##
```{r bias_setup, include=FALSE}

bias_list <- cite_df %>% filter(bias == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r bias_list`

{{% toc %}}

### Critical Race Theory ##
```{r crt_setup, include=FALSE}

crt_list <- cite_df %>% filter(crt == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r crt_list`

{{% toc %}}

### Systems, Constructs, and Frameworks ##
```{r systems_setup, include=FALSE}

syst_list <- cite_df %>% filter(systems == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r syst_list`

{{% toc %}}

### Thoughts on Diversity, Equity, &/or Inclusion ##
```{r dei_setup, include=FALSE}

dei_list <- cite_df %>% filter(dei == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r dei_list`

{{% toc %}}

### Misc ##
```{r misc_setup, include=FALSE}

misc_list <- cite_df %>% filter(health == FALSE & edu == FALSE & women == FALSE & academy == FALSE
                                & disabil == FALSE & race == FALSE & LGBT == FALSE & dei == FALSE &
                                crt == FALSE & systems == FALSE & mentor == FALSE) %>% 
  pull(full_cite) %>% paste(., collapse = "\n")
```

`r misc_list`

{{% toc %}}
