---
title: "Diversify Digest"
author: admin
date: Sys.Date
output: md_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')

library(tidyverse)
library(lubridate)

today <- Sys.Date()

raw_data <- read_csv(paste0("../data/raw", today, ".csv"))

#Category terms----
LGBT_terms <- c("Lgbt|Trans |Transgender|Queer|Sexual Minorit|Gender Minorit|Gender Ident|Sexual Orientation|Lesbian|Gay")

race_terms <- c("Urm|Race|Ethnicity|Ethnic|Black|Asian|Native|Indige|Hurm|Immigrant|Racial|Latin|Hispanic|Minority|Racism")

disabil_terms <- c("Disabil|Ability|Deaf|Blind|Wheelchair|Autis|Neuro|Accessibility|Mental Illness|Ablism|Impaired|Adhd|Disable")

women_terms <- c("Gender|Women|Female")

edu_terms <- c("Education|Academic|High School|Elementary|Middle School|School|College Grad|Classroom|Learning|Pedagog|Teach|Instruct|Curric|Affirmative Action|Campus")

health_terms <- c("Healthcare|Health|Care|Physician|Illness|Disease|Pain|Medic|Provid|Nurse|Doctor|Resident|Patient|Treat")

acad_terms <- c("Grad|Postdoc|Faculty|Academia|Research|Academy|Journal|Publish|Public|Cite|Citation|Author|Academic|Review|Higher Ed|Peer Review|Lit|Editor")

ment_terms <- c("Mentor|Network")

crt_terms <- c("Critical Race|Crt|Race Theory|Anti")

syst_terms <- c("System|Construct|Frame|Research")

bias_terms <- c("Bias|Implicit|Stereotype|Training|Workshop")

#Categorize titles & generate string----
cite_df <- raw_data %>% mutate(full_cite = paste0("[", title, "](", url, ") ", author, "\n"),
                               race = str_detect(keywords, race_terms),
                               LGBT = str_detect(keywords, LGBT_terms),
                               disabil = str_detect(keywords, disabil_terms),
                               women = str_detect(keywords, women_terms),
                               edu = str_detect(keywords, edu_terms),
                               health = str_detect(keywords, health_terms),
                               academy = str_detect(keywords, acad_terms),
                               mentor = str_detect(keywords, ment_terms),
                               crt = str_detect(keywords, crt_terms),
                               systems = str_detect(keywords, syst_terms),
                               bias = str_detect(keywords, bias_terms),
                               dei = if_else(str_detect(keywords, "Diversity") & str_detect(keywords, "Inclusion"), TRUE, FALSE))

```
\-\-\- 

title: `r paste0(month(today, label = TRUE), " ", day(today), " Digest")`

date: `r today`

authors: 

\-\-\- 

{{% toc %}}

### Sexual & Gender Minorities (e.g, LGBTQA+) ##
```{r lgbt_setup, include=FALSE}

LGBT_list <- cite_df %>% filter(LGBT == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r LGBT_list`

### Race/Ethnicity ##
```{r race_setup, include=FALSE}

race_list <- cite_df %>% filter(race == TRUE & crt == FALSE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r race_list`

{{% toc %}}

### Disabilities ##
```{r disabil_setup, include=FALSE}

disabil_list <- cite_df %>% filter(disabil == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r disabil_list`

{{% toc %}}

### Women ##
```{r women_setup, include=FALSE}

women_list <- cite_df %>% filter(women == TRUE & health == FALSE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r women_list`

{{% toc %}}

### Education & Curriculum ##
```{r edu_setup, include=FALSE}

edu_list <- cite_df %>% filter(edu == TRUE & academy == FALSE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r edu_list`

{{% toc %}}

### Healthcare & Medical School ##
```{r health_setup, include=FALSE}

health_list <- cite_df %>% filter(health == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r health_list`

{{% toc %}}

### Academia & Publishing ##
```{r acad_setup, include=FALSE}

acad_list <- cite_df %>% filter(academy == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r acad_list`

{{% toc %}}

### Mentoring ##
```{r ment_setup, include=FALSE}

ment_list <- cite_df %>% filter(mentor == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r ment_list`

{{% toc %}}

### Implicit Bias & Stereotypes: Research, Training & Workshops ##
```{r bias_setup, include=FALSE}

bias_list <- cite_df %>% filter(bias == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r bias_list`

{{% toc %}}

### Anti-Racism & Critical Race Theory ##
```{r crt_setup, include=FALSE}

crt_list <- cite_df %>% filter(crt == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r crt_list`

{{% toc %}}

### Research Tools: Systems, Constructs, & Frameworks ##
```{r systems_setup, include=FALSE}

syst_list <- cite_df %>% filter(systems == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r syst_list`

{{% toc %}}

### Thoughts on Diversity, Equity, &/or Inclusion ##
```{r dei_setup, include=FALSE}

dei_list <- cite_df %>% filter(dei == TRUE) %>% pull(full_cite) %>% paste(., collapse = "\n")
```

`r dei_list`

{{% toc %}}

### Misc ##
```{r misc_setup, include=FALSE}

misc_list <- cite_df %>% filter(health == FALSE & edu == FALSE & women == FALSE & academy == FALSE
                                & disabil == FALSE & race == FALSE & LGBT == FALSE & dei == FALSE &
                                crt == FALSE & systems == FALSE & mentor == FALSE & bias == FALSE) %>% 
  pull(full_cite) %>% paste(., collapse = "\n")
```

`r misc_list`

{{% toc %}}
